Relevance-based Quantization of Scattering Features for Unsupervised Mining of Environmental Audio

### 2018-02-21 paper/structureScene.tex
TODO added

As seen in Figure \ref{fig:ASS_-1}, the BOF approach behaves similarly to the early approach when applied to MFCCs. In contrast, its performance decreases compared to the early approach when applied to scattering features. Extensive analysis of those results is out of the scope of this paper, but this likely results from the dimension reduction applied prior to estimating the GMMs in the BOF model.

>>>>

As seen in Figure \ref{fig:ASS_-1}, the BOF approach behaves similarly to the early approach when applied to the two types of features.

TODO ML comment new figure
